Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2020-08-19 mice_synthesizing/paper.Rmd
Update intro.

The R-package `mice` [@mice] implements the fully conditional specification approach for missing data. Since the imputation approaches for missing data and synthetic data do not differ in terms of the imputation process, `mice` can be used for creating synthetic data as well, which will be shown in more detail in the remainder of this paper. Additionally, it will be shown that creating confidence valid [TO DO: FULLY/PARTIALLY] synthetic data can be generated by means of `mice`. However, before introducing `mice` for the creation of synthetic data, the pooling rules for synthetic data will be discussed.

-- -- EXPLAIN MICE -- --

@@

## Methods
Boys data - bootstrapped to obtain a population.

@@

**Explain approach**

**INTRO**

- think about fully / partially synthetic data.
- explain the procedure of creating synthetic datasets
- introduce mice for imputation of missing data
- mice can also be used for the imputation of synthetic data
- brief introduction of the mice algorithm???

**METHODS**

- explain simple synthetic data example
- explain imputation settings
- CART has been proposed by Reiter

>>>>

The R-package `mice` [@mice] implements the fully conditional specification approach for missing data. Since the imputation approaches for missing data and synthetic data do not differ in terms of the imputation process, `mice` can be used for creating synthetic data as well, which will be shown in more detail in the remainder of this paper. In the next section, the pooling rules that are required to obtain inferences from the synthetic datasets are discussed. Thereafter, it will be shown that creating confidence valid [TO DO: FULLY/PARTIALLY] synthetic data can be generated by means of `mice`. Also, it is shown that iterating over the conditional distributions in order to establish convergence is not required, due to the fact that new values are drawn directly from posterior distribution given the observed data.

@@

## Methods

- Boys data - bootstrapped to obtain a population.
- explain simple synthetic data procedure
- explain imputation settings
- CART has been proposed by Reiter

@@
